The EAGLE Data Aggregator: Data Quality Monitoring

### 2016-01-24 source/CNR/TheEAGLEDataAggregatorDataQualityMonitoring.tex
finished posters and committee, compiled the all lot
I have Moved all the compiled articles in the pdfs folder and compiled
with all bits and pieces
Paper CNR (Mannocci et al) edited and added to the pdfs folder

%%%%%%%%
%AUTHORS:%
%%%%%%%%
\author[CNR-ISTI]{Andrea Mannocci\corref{all}}
\author[CNR-ISTI]{Vittore Casarosa}
\author[CNR-ISTI]{Paolo Manghi}
\author[CNR-ISTI]{Franco Zoppi}

%Additional information about corresponding author, addresses and affiliations:
\cortext[all]{\{andrea.mannocci, vittore.casarosa, paolo.manghi, franco.zoppi\}@isti.cnr.it
}

@@

The EAGLE project (fully described in \citep{eagle}) aggregates epigraphy related content from about 20 different data providers (cultural institutions all over Europe), and makes its content available to both Europeana \citep{europeana} (through an OAI-PMH interface) and to scholars and the general public through a Web portal.

@@

The interaction between the IQM and the Monitoring Framework is done through a user friendly user interface (WebUI) provided by the DFDS. In addition to providing easy access to the observation time series, the WebUI provides the facilities to define the overall Monitoring Scenario, which will include the sensors and the controls.

@@

\bibliographystyle{sapauth-eng}
\bibliography{EAGLE}

>>>>

%%%%%%%%
%AUTHORS:%
%%%%%%%%
\author[CNR-ISTI]{Andrea Mannocci\corref{all}}
\author[CNR-ISTI]{Vittore Casarosa\corref{all}}
\author[CNR-ISTI]{Paolo Manghi\corref{all}}
\author[CNR-ISTI]{Franco Zoppi\corref{all}}

%Additional information about corresponding author, addresses and affiliations:
\cortext[all]{Corresponding authors: \{andrea.mannocci, vittore.casarosa, paolo.manghi, franco.zoppi\}@isti.cnr.it
}

@@

The EAGLE project \citep[fully described in][]{eagle} aggregates epigraphy related content from about 20 different data providers (cultural institutions all over Europe), and makes its content available to both Europeana \citep{europeana} (through an OAI-PMH interface) and to scholars and the general public through a Web portal.

@@

The interaction between the IQM and the Monitoring Framework is done through a user friendly user interface (WebUI) provided by the DFDS. In addition to providing easy access to the observation time series, the WebUI provides the facilities to define the overall Monitoring Scenario, which will include the sensors and the \emph{controls}.

@@

\bibliographystyle{sapauth-eng}
\bibliography{../../EAGLE}
